Galaxy Zoo: Morphological Classifications for Galaxies in HST Legacy Imaging

### 2016-03-23 writeup/gz_hubble_data.tex
Finished the fake AGN tables and fixed some errors.

\begin{table*}
\caption{Summary of Galaxy Zoo: Hubble imaging \label{gzh_numbers}}
\begin{tabular}{lclcrr}
\hline\hline
Survey &  $t_{\rm exp}$ & Filters & Resolution & Area & $N_{\rm galaxies}$ \\
 & [sec] & & [\arcsec/pix] & [arcmin$^2$] & \\
\hline
AEGIS                         & 2100$-$2300 & \Vband{} and \Iband{}            & 0.03 & 710   & 8157  \\
COSMOS                        & 2028        & \Iband{}                         & 0.05 & 6480  & 88530 \\
GEMS                          & 2160$-$2286 & \Vband{} and \zband{}            & 0.03 & 800   & 9143  \\
GOODS                         & 1000$-$2100 & \Bband, \Vband, \iband, \zband{} & 0.03 & 320   & 7336  \\
\hspace{10pt} \emph{GOODS-N}  & $-$         & $-$                              & $-$  & $-$   & \emph{2551}  \\
\hspace{10pt} \emph{GOODS-S}  & $-$         & $-$                              & $-$  & $-$   & \emph{4785}  \\
\hline
total                         & $-$         & $-$                              & $-$  & 8310  & 113166  \\
\hline\hline
\end{tabular}
\end{table*}

@@

\tabletypesize{\scriptsize}
\begin{deluxetable}{l|rr|rrr|rr|r|rr}

\centering
%\rotate
\tablecolumns{12}
\tablewidth{0pc}
\tablecaption{GZH redshifts by survey} 
\label{tbl:redshifts}
\tabletypesize{\scriptsize}
\tablehead{
 &   
\multicolumn{2}{c}{\underline{Griffith}} &
\multicolumn{3}{c}{\underline{3DHST}} &
\multicolumn{2}{c}{\underline{MUSYC}} &
\multicolumn{1}{c}{\underline{UltraVISTA}}&
\multicolumn{2}{c}{\underline{Total}} 
\\
\colhead{Survey} & 
\colhead{spec-z} & 
\colhead{photo-z} & 
\colhead{spec-z} & 
\colhead{grism-z} & 
\colhead{photo-z} & 
\colhead{spec-z} & 
\colhead{photo-z} & 
\colhead{photo-z} & 
\colhead{with redshift} &
\colhead{in survey}
}
\small
\startdata
%Survey     Gs        Gp    3ds    3dg     3dp       Ms      Mp       UVp       total
AEGIS    & 3,656  & 2,941  & 12  &  515  &  249    & 0     & 0     &  0      & 7,373  & 8,507\\
COSMOS   & 7,201  & 77,435 & 35  &  358  &  26     & 0     & 0     &  2,665  & 85,020 & 92,808 \\
GEMS     & 387    & 628    & 6   &  99   &  40     & 279   & 7,304 & 0       & 8,743  & 9,304\\
GOODS-N  & 1,947  & 37     & 418 & 1,545 &  1,381  & 0     & 0     & 0       & 5,328  & 12,030 \\
GOODS-S  & 1,080  & 4      & 327 & 1,348 &  281    & 816   & 1,184 & 0       & 5,040  & 10,284 \\
SDSS     & 0      & 0      & 0   &  0    &  0      & 0     & 0     & 0       & 37,545 & 51,861  \\
\hline
Total    & 14,271 & 81,045 & 798 & 3,865 & 1,977   & 1,095 & 8,488 & 2,665   & 114,204 & 184,794\\
\enddata
\end{deluxetable}

@@

The selection criteria for the different morphological categories is summarised in Table \ref{morphologies}. The surface brightness selection ($N_\mu = 3$) was (1) low: $\mu > 21.5$~\magarc;  (2) mid: $20.5 < \mu < 21.5$~\magarc; and (3) high: $\mu < 20.5$~\magarc. For each of the four ``target redshifts'' ($z = 0.3, 0.5, 0.8$ and $1.0$), the images were redshifted in $\Delta z = 0.1$ bins up to $z=1.0$.

\begin{table*}
\caption{Summary of morphological categories selected for FERENGI sample.\label{morphologies}}
\begin{tabular}{lllc}
\hline\hline
Morphology          & Label &  Selection                                                                                            & $N_{\rm objects}$ \\
                    &       &                                                                                                       & [$N_z \times N_\mu$] \\
\hline
Features            & Yes       & $p_{\rm features} > 0.8$, $p_{\rm odd} < 0.1$                                                         & 12 \\ 
                    & Int.      & $0.3 < p_{\rm smooth} < 0.6$, $p_{\rm odd} < 0.1$                                                     & 12 \\ 
                    & No        & $p_{\rm smooth} > 0.8$, $p_{\rm odd} < 0.1$                                                           & 12 \\ 
Merger              & No        & $p_{\rm features} > 0.8$, $p_{\rm odd < 0.1}$, $p_{\rm merger} < 0.1$                                 & 12 \\
                    & Int.      & $p_{\rm odd} > 0.5$, $0.1< p_{\rm merger} < 0.4$                                                      & 12 \\ 
                    & Yes       & $p_{\rm odd} > 0.5$, $p_{\rm merger} > 0.4$                                                           & 12 \\
Edge-on             & Yes       & $p_{\rm edgeon} > 0.8$, $p_{\rm features} > 0.5$                                                      & 12 \\
                    & Int.      & $0.4 < p_{\rm edgeon} < 0.8$ , $p_{\rm features} > 0.5$                                               & 12 \\
                    & No        & $p_{\rm edgeon} < 0.2$, $p_{\rm features} > 0.5$                                                      & 12 \\
Bar                 & No        & $p_{\rm bar} < 0.1$, $p_{\rm features} > 0.5$, $p_{\rm edgeon} < 0.2$                                 & 24 \\
                    & Int.      & $0.2 < p_{\rm bar} < 0.4$, $p_{\rm features} > 0.5$, $p_{\rm edgeon} < 0.2$                           & 24 \\
                    & Yes       & $p_{\rm bar} > 0.8$, $p_{\rm features} > 0.5$, $p_{\rm edgeon} < 0.2$                                 & 24 \\
Visible spiral      & No        & $p_{\rm spiral} < 0.2$, $p_{\rm features} > 0.5$, $p_{\rm edgeon} < 0.2$, $p_{\rm bar} < 0.1$         & 12 \\
                    & Int.      & $0.2 < p_{\rm spiral} < 0.8$, $p_{\rm features} > 0.5$, $p_{\rm edgeon} < 0.2$, $p_{\rm bar} < 0.1$   & 12 \\
                    & Yes       & $p_{\rm spiral} > 0.8$, $p_{\rm features} > 0.5$, $p_{\rm edgeon} < 0.2$, $p_{\rm bar} < 0.1$         & 12 \\
Oblique bulge size  & No        & $p_{\rm nobulge>0.6}$, $p_{\rm features} > 0.5$, $p_{\rm edgeon} < 0.5$, $p_{\rm bar} < 0.2$          & 12 \\
                    & Int.      & $p_{\rm justnoticeable}>0.6$, $p_{\rm features} > 0.5$, $p_{\rm edgeon} < 0.5$, $p_{\rm bar} < 0.2$   & 12 \\
                    & Yes       & $p_{\rm obvious|dominant}>0.5$, $p_{\rm features} > 0.5$, $p_{\rm edgeon} < 0.5$, $p_{\rm bar} < 0.2$ & 12 \\
Edge-on bulge shape & Round     & $p_{\rm rounded}>0.5$, $p_{\rm features} > 0.5$, $p_{\rm edgeon} > 0.5$                               & 12 \\
                    & Boxy      & $p_{\rm boxy}>0.4$, $p_{\rm features} > 0.5$, $p_{\rm edgeon} > 0.2$                                  & 12 \\
                    & No bulge  & $p_{\rm nobulge}>0.5$, $p_{\rm features} > 0.5$, $p_{\rm edgeon} > 0.5$                               & 12 \\
\hline\hline
\end{tabular}
\end{table*}

@@

The final number of \ferengi{} images produced for each galaxy is ultimately a function of galaxy's redshift, since the new images cannot be resampled at better angular resolution than the original SDSS data, as well as the number of $e$ values selected. Table~\ref{ferengivalues} summarizes the total sample of redshifted images produced for GZH.

\begin{table}
\caption{Summary of FERENGI artificial redshifting \label{ferengivalues}}
\begin{tabular}{lccccr}
\hline\hline
$z_{\rm target}$ & $N_{z {\rm bins}}$ & $N_{\rm evolution}$ & $e_{\rm max}$ & $N_{\rm galaxies}$ & $N_{\rm images}$\\
\hline
0.3              & 8                  & 7                   & $-3.0$        & 72             & 4032 \\
0.5              & 6                  & 4                   & $-1.5$        & 72             & 1728 \\
0.8              & 3                  & 3                   & $-1.0$        & 72             &  648 \\
1.0              & 1                  & 3                   & $-1.0$        & 72             &  216 \\
\hline\hline
\end{tabular}
\end{table}

@@

In Figure~\ref{fig:p_vs_p} we examine the change in $p_{\rm features}$ for the \ferengi{} galaxies relative to their lowest simulated redshift. In this analysis, only galaxies whose lowest simulated redshift image was ($\rm z_{sim}=0.3$) were used (see Table \ref{ferengivalues}), and only those which had detectable surface brightness measurements in \sextractor{}; this includes 3,950 of the total 6,466 images. For each simulated redshift value $z$, and at a fixed surface brightness $\mu$, we plot $p_{\rm features,z}$, the value measured at that simulated redshift, vs $p_{\rm features,z=0.3}$, the value measured for the same galaxy imaged at $z=0.3$.

@@

\begin{table}ー
\caption{Distribution of \ferengi{} images analysed in Figure~\ref{fig:p_vs_p}. Correctable images had a single-valued relationship between their measured $p_{\rm features}$ values at high and low redshifts (white regions in Figure~\ref{fig:p_vs_p}). Uncorrectable images had a non single-valued relationship (blue regions). NEI images had undetermined relationships due to a lack of data ($N<5$) in their corresponding z-$\mu$ bins (gray regions).   \label{ferengi_corrections}}
\begin{tabular}{lrr}
\hline \hline
				                   & N       & \% \\
\hline 
Correctable                        & 1,884   & 48\% \\
Uncorrectable                      & 1,986   & 50\% \\
NEI                                & 80     &  2\%\\
Total                              & 3,950   & 100\% \\
\hline \hline
\end{tabular}
\end{table}

@@

\begin{itemize}
\item talk about where the Hubble sample falls in this space, reference table \ref{tbl:hubble_debiasable} 
\item justify $N>5$ and spread $< 0.2$ (or find a better way to choose criteria)
\item check out corrections for correctable and NEI, show some sample images of corrected galaxies
\item show some data for $\pbar$, determine or justify why we won't debiase them  
\end{itemize}

@@

\section{The Catalog}

The data release for GZH includes morphological data for 181,101 galaxies. The full table can be accessed at some website. We also include a secondary metadata table, which contains data from a variety of sources explained in Section \ref{sec:data}.

For each galaxy we list its unique objid, as well as the source's RA, DEC, and survey (AEGIS, COSMOS, GEMS, GOODS North (full and shallow depth), GOODS South (full and shallow depth), SDSS. For each of the 40 (?) questions in the GZH decision tree, the following classification data is provided: For each question, $\tt N_{votes}$ is the number of users to answer that question. For each unique answer, $\tt fraction$ is the fraction of users to select that answer ($\rm N_{answer}/N_{votes}$, and $\tt weighted$ is the weighted fraction, which takes into account user consistency (Section~\ref{sec:weighting}).

@@

\tabletypesize{\scriptsize}
\begin{deluxetable}{lllllcrllllll|c}
\centering
\rotate
\tablecolumns{13}
\tablewidth{0pc}
\tablecaption{GZH morphological classifications for AEGIS, COSMOS, GEMS, and GOODS images} 
\label{tbl:catalog}
\tabletypesize{\scriptsize}
\tablehead{
 & & & RA & dec  &  
\multicolumn{2}{c}{\underline{t01\_smooth\_or\_features\_}} &
\multicolumn{6}{c}{\underline{t01\_smooth\_or\_features\_a01\_smooth\_}} &
\colhead{$\ldots$}
\\
\colhead{Project ID} & 
\colhead{Hubble ID} & 
\colhead{Imaging} & 
\colhead{J2000} & 
\colhead{J2000} & 
\colhead{Correction$^{1}$} & 
\colhead{$N_\mathrm{votes}$} & 
\colhead{fraction} & 
\colhead{weighted} & 
\colhead{debiased} & 
\colhead{best} &
\colhead{lower~limit} & 
\colhead{upper~limit} &
\colhead{}
}
\small
\startdata
AHZ100002g  & 10010842  & AEGIS             &          &            & 0        & 948       & 0.118    & 0.128     & 0.085    & 0.085    & 0.226     & 0.226    \\
AHZ100002h  & 10010870  & AEGIS             &          &            & 4        & 429       & 0.567    & 0.592     & 0.927    & 0.592    & $-$       & $-$      \\
$\ldots$    & $\ldots$  & $\ldots$          & $\ldots$ & $\ldots$   & $\ldots$ &  $\ldots$ & $\ldots$ & $\ldots$  & $\ldots$ & $\ldots$ & $\ldots$  & $\ldots$ \\
AHZ20004kd  & 20014731  & COSMOS            &          &            & 3        & 185       & 0.682    & 0.675     & 0.147    & 0.675    & $-$       & $-$      \\
AHZ20004ke  & 20014732  & COSMOS            &          &            & 2        & 149       & 0.689    & 0.756     & 0.893    & 0.756    & $-$       & $-$      \\
$\ldots$    & $\ldots$  & $\ldots$          & $\ldots$ & $\ldots$   & $\ldots$ &  $\ldots$ & $\ldots$ & $\ldots$  & $\ldots$ & $\ldots$ & $\ldots$  & $\ldots$ \\
AHZ400043g  & 90022729  & GEMS              &          &            & 1        & 400       & 0.702    & 0.733     & 0.487    & 0.734    & 0.483     & 0.800    \\
AHZ4000416  & 90022735  & GEMS              &          &            & 1        & 463       & 0.646    & 0.698     & 0.508    & 0.698    & 0.171     & 0.727    \\
$\ldots$    & $\ldots$  & $\ldots$          & $\ldots$ & $\ldots$   & $\ldots$ &  $\ldots$ & $\ldots$ & $\ldots$  & $\ldots$ & $\ldots$ & $\ldots$  & $\ldots$ \\
AGZ0007z47  & 10014     & GOODS-N-FULLDEPTH &          &            & 1        & 40        & 0.475    & 0.475     & 0.197    & 0.475    & 0.011     & 0.496    \\
AGZ0007z48  & 10017     & GOODS-N-FULLDEPTH &          &            & 3        & 40        & 0.675    & 0.675     & 0.048    & 0.675    & 0.168     & 0.669    \\
$\ldots$    & $\ldots$  & $\ldots$          & $\ldots$ & $\ldots$   & $\ldots$ &  $\ldots$ & $\ldots$ & $\ldots$  & $\ldots$ & $\ldots$ & $\ldots$  & $\ldots$ \\
AGZ00083jb  & 8869      & GOODS-S-FULLDEPTH &          &            & 1        & 40        & 0.425    & 0.425     & 0.109    & 0.425    & 0.070     & 0.548    \\
AGZ00083jc  & 8878      & GOODS-S-FULLDEPTH &          &            & 0        & 40        & 0.205    & 0.205     & 0.048    & 0.048    & $-$0.005  & 0.287    \\
\enddata
\tablenotetext{1}{Flag indicating how the vote fractions for this galaxy were corrected through debiasing (\S\ref{ssec:zeta_results}), if possible. 0~=~correctable, 1~=~uncorrectable ($p_{raw}$ --- $p_{adj}$ is not single-valued), 2~=~uncorrected ($z_{\rm gal} < 0.3$), 3~=~uncorrectable (insufficient FERENGI galaxies in this $z$-$\mu$ bin), 4~=~uncorrectable (no galaxy redshift available).}
\tablecomments{The full version of this table is available in electronic form, as well as at \url{http://data.galaxyzoo.org}. The complete version includes data for 118,425~galaxies and morphological information for all tasks in the tree. A subset of the information is shown here to illustrate form and content.}
\end{deluxetable}

@@

Needs some test cases for extracting a given set of objects (eg, clump galaxies in a particular redshift range) and evaluation of the results. Possibly include suggested thresholds, \'a la GZ2. 
\section{Using the catalog}
\label{sec:cookbook}
Include cookbook for selecting morphologies. 
\section{Analysis}

@@

\section{Summary}

@@

\begin{table}
\caption{Breakdown of what we can correct out of the GOODS shallow depth data. \label{goods_shallow_categories}}
\begin{tabular}{lrrrrrrrr}
\hline\hline
                                   & GOODS-N & GOODS-S & Total \\
\hline
Correctable                        & 748     & 514     & 1,262 \\
Uncorrectable                      & 526     & 1,143   & 1,669 \\
No Correction Needed ($z \le 0.3$) & 267     & 267     & 534   \\ 
NEI                                & 851     & 2,670   & 3,521 \\
No Redshift Information            & 159     & 319     & 478   \\
Total                              & 2,551   & 4,913   & 7,464 \\
\hline\hline
\end{tabular}
\end{table}

>>>>

\begin{table*}
\caption{Summary of Galaxy Zoo: Hubble imaging \label{tbl:gzh_numbers}}
\begin{tabular}{lclcrr}
\hline\hline
Survey &  $t_{\rm exp}$ & Filters & Resolution & Area & $N_{\rm galaxies}$ \\
 & [sec] & & [\arcsec/pix] & [arcmin$^2$] & \\
\hline
AEGIS                         & 2100$-$2300 & \Vband{} and \Iband{}            & 0.03 & 710   & 8157  \\
COSMOS                        & 2028        & \Iband{}                         & 0.05 & 6480  & 88530 \\
GEMS                          & 2160$-$2286 & \Vband{} and \zband{}            & 0.03 & 800   & 9143  \\
GOODS                         & 1000$-$2100 & \Bband, \Vband, \iband, \zband{} & 0.03 & 320   & 7336  \\
\hspace{10pt} \emph{GOODS-N}  & $-$         & $-$                              & $-$  & $-$   & \emph{2551}  \\
\hspace{10pt} \emph{GOODS-S}  & $-$         & $-$                              & $-$  & $-$   & \emph{4785}  \\
\hline
total                         & $-$         & $-$                              & $-$  & 8310  & 113166  \\
\hline\hline
\end{tabular}
\end{table*}

@@

\tabletypesize{\scriptsize}
\begin{deluxetable}{l|rr|rrr|rr|r|rr}
\centering
%\rotate
\tablecolumns{12}
\tablewidth{0pc}
\tablecaption{GZH redshifts by survey\label{tbl:redshifts}} 
\tabletypesize{\scriptsize}
\tablehead{
 &   
\multicolumn{2}{c}{\underline{Griffith}} &
\multicolumn{3}{c}{\underline{3DHST}} &
\multicolumn{2}{c}{\underline{MUSYC}} &
\multicolumn{1}{c}{\underline{UltraVISTA}}&
\multicolumn{2}{c}{\underline{Total}} 
\\
\colhead{Survey} & 
\colhead{spec-z} & 
\colhead{photo-z} & 
\colhead{spec-z} & 
\colhead{grism-z} & 
\colhead{photo-z} & 
\colhead{spec-z} & 
\colhead{photo-z} & 
\colhead{photo-z} & 
\colhead{with redshift} &
\colhead{in survey}
}
\small
\startdata
%Survey     Gs        Gp    3ds    3dg     3dp       Ms      Mp       UVp       total
AEGIS    & 3,656  & 2,941  & 12  &  515  &  249    & 0     & 0     &  0      & 7,373  & 8,507\\
COSMOS   & 7,201  & 77,435 & 35  &  358  &  26     & 0     & 0     &  2,665  & 85,020 & 92,808 \\
GEMS     & 387    & 628    & 6   &  99   &  40     & 279   & 7,304 & 0       & 8,743  & 9,304\\
GOODS-N  & 1,947  & 37     & 418 & 1,545 &  1,381  & 0     & 0     & 0       & 5,328  & 12,030 \\
GOODS-S  & 1,080  & 4      & 327 & 1,348 &  281    & 816   & 1,184 & 0       & 5,040  & 10,284 \\
SDSS     & 0      & 0      & 0   &  0    &  0      & 0     & 0     & 0       & 37,545 & 51,861  \\
\hline
Total    & 14,271 & 81,045 & 798 & 3,865 & 1,977   & 1,095 & 8,488 & 2,665   & 114,204 & 184,794\\
\enddata
\end{deluxetable}

@@

The selection criteria for the different morphological categories is summarised in Table \ref{tbl:morphologies}. The surface brightness selection ($N_\mu = 3$) was (1) low: $\mu > 21.5$~\magarc;  (2) mid: $20.5 < \mu < 21.5$~\magarc; and (3) high: $\mu < 20.5$~\magarc. For each of the four ``target redshifts'' ($z = 0.3, 0.5, 0.8$ and $1.0$), the images were redshifted in $\Delta z = 0.1$ bins up to $z=1.0$.

\begin{table*}
\caption{Summary of morphological categories selected for FERENGI sample.\label{tbl:morphologies}}
\begin{tabular}{lllc}
\hline\hline
Morphology          & Label &  Selection                                                                                            & $N_{\rm objects}$ \\
                    &       &                                                                                                       & [$N_z \times N_\mu$] \\
\hline
Features            & Yes       & $p_{\rm features} > 0.8$, $p_{\rm odd} < 0.1$                                                         & 12 \\ 
                    & Int.      & $0.3 < p_{\rm smooth} < 0.6$, $p_{\rm odd} < 0.1$                                                     & 12 \\ 
                    & No        & $p_{\rm smooth} > 0.8$, $p_{\rm odd} < 0.1$                                                           & 12 \\ 
Merger              & No        & $p_{\rm features} > 0.8$, $p_{\rm odd < 0.1}$, $p_{\rm merger} < 0.1$                                 & 12 \\
                    & Int.      & $p_{\rm odd} > 0.5$, $0.1< p_{\rm merger} < 0.4$                                                      & 12 \\ 
                    & Yes       & $p_{\rm odd} > 0.5$, $p_{\rm merger} > 0.4$                                                           & 12 \\
Edge-on             & Yes       & $p_{\rm edgeon} > 0.8$, $p_{\rm features} > 0.5$                                                      & 12 \\
                    & Int.      & $0.4 < p_{\rm edgeon} < 0.8$ , $p_{\rm features} > 0.5$                                               & 12 \\
                    & No        & $p_{\rm edgeon} < 0.2$, $p_{\rm features} > 0.5$                                                      & 12 \\
Bar                 & No        & $p_{\rm bar} < 0.1$, $p_{\rm features} > 0.5$, $p_{\rm edgeon} < 0.2$                                 & 24 \\
                    & Int.      & $0.2 < p_{\rm bar} < 0.4$, $p_{\rm features} > 0.5$, $p_{\rm edgeon} < 0.2$                           & 24 \\
                    & Yes       & $p_{\rm bar} > 0.8$, $p_{\rm features} > 0.5$, $p_{\rm edgeon} < 0.2$                                 & 24 \\
Visible spiral      & No        & $p_{\rm spiral} < 0.2$, $p_{\rm features} > 0.5$, $p_{\rm edgeon} < 0.2$, $p_{\rm bar} < 0.1$         & 12 \\
                    & Int.      & $0.2 < p_{\rm spiral} < 0.8$, $p_{\rm features} > 0.5$, $p_{\rm edgeon} < 0.2$, $p_{\rm bar} < 0.1$   & 12 \\
                    & Yes       & $p_{\rm spiral} > 0.8$, $p_{\rm features} > 0.5$, $p_{\rm edgeon} < 0.2$, $p_{\rm bar} < 0.1$         & 12 \\
Oblique bulge size  & No        & $p_{\rm nobulge>0.6}$, $p_{\rm features} > 0.5$, $p_{\rm edgeon} < 0.5$, $p_{\rm bar} < 0.2$          & 12 \\
                    & Int.      & $p_{\rm justnoticeable}>0.6$, $p_{\rm features} > 0.5$, $p_{\rm edgeon} < 0.5$, $p_{\rm bar} < 0.2$   & 12 \\
                    & Yes       & $p_{\rm obvious|dominant}>0.5$, $p_{\rm features} > 0.5$, $p_{\rm edgeon} < 0.5$, $p_{\rm bar} < 0.2$ & 12 \\
Edge-on bulge shape & Round     & $p_{\rm rounded}>0.5$, $p_{\rm features} > 0.5$, $p_{\rm edgeon} > 0.5$                               & 12 \\
                    & Boxy      & $p_{\rm boxy}>0.4$, $p_{\rm features} > 0.5$, $p_{\rm edgeon} > 0.2$                                  & 12 \\
                    & No bulge  & $p_{\rm nobulge}>0.5$, $p_{\rm features} > 0.5$, $p_{\rm edgeon} > 0.5$                               & 12 \\
\hline\hline
\end{tabular}
\end{table*}

@@

The final number of \ferengi{} images produced for each galaxy is ultimately a function of galaxy's redshift, since the new images cannot be resampled at better angular resolution than the original SDSS data, as well as the number of $e$ values selected. Table~\ref{tbl:ferengivalues} summarizes the total sample of redshifted images produced for GZH.

\begin{table}
\caption{Summary of FERENGI artificial redshifting \label{tbl:ferengivalues}}
\begin{tabular}{lccccr}
\hline\hline
$z_{\rm target}$ & $N_{z {\rm bins}}$ & $N_{\rm evolution}$ & $e_{\rm max}$ & $N_{\rm galaxies}$ & $N_{\rm images}$\\
\hline
0.3              & 8                  & 7                   & $-3.0$        & 72             & 4032 \\
0.5              & 6                  & 4                   & $-1.5$        & 72             & 1728 \\
0.8              & 3                  & 3                   & $-1.0$        & 72             &  648 \\
1.0              & 1                  & 3                   & $-1.0$        & 72             &  216 \\
\hline\hline
\end{tabular}
\end{table}

@@

In Figure~\ref{fig:p_vs_p} we examine the change in $p_{\rm features}$ for the \ferengi{} galaxies relative to their lowest simulated redshift. In this analysis, only galaxies whose lowest simulated redshift image was ($\rm z_{sim}=0.3$) were used (see Table \ref{tbl:ferengivalues}), and only those which had detectable surface brightness measurements in \sextractor{}; this includes 3,950 of the total 6,466 images. For each simulated redshift value $z$, and at a fixed surface brightness $\mu$, we plot $p_{\rm features,z}$, the value measured at that simulated redshift, vs $p_{\rm features,z=0.3}$, the value measured for the same galaxy imaged at $z=0.3$.

@@

\begin{table}
\caption{Distribution of \ferengi{} images analysed in Figure~\ref{fig:p_vs_p}. Correctable images had a single-valued relationship between their measured $p_{\rm features}$ values at high and low redshifts (white regions in Figure~\ref{fig:p_vs_p}). Uncorrectable images had a non single-valued relationship (blue regions). NEI images had undetermined relationships due to a lack of data ($N<5$) in their corresponding z-$\mu$ bins (gray regions).\label{tbl:ferengi_corrections}}
\begin{tabular}{lrr}
\hline \hline
				                   & N       & \% \\
\hline 
Correctable                        & 1,884   & 48\% \\
Uncorrectable                      & 1,986   & 50\% \\
NEI                                & 80     &  2\%\\
Total                              & 3,950   & 100\% \\
\hline \hline
\end{tabular}
\end{table}

@@

\begin{itemize}
\item talk about where the Hubble sample falls in this space, reference Table~\ref{tbl:hubble_debiasable} 
\item justify $N>5$ and spread $< 0.2$ (or find a better way to choose criteria)
\item check out corrections for correctable and NEI, show some sample images of corrected galaxies
\item show some data for $\pbar$, determine or justify why we won't debias them  
\end{itemize}

@@

We also classified a set of images designed to measure the effect of AGN on morphological classifications. This could occur since galactic nuclei can have bright, unresolved optical emission that could either mimic the effect of a strong bulge or otherwise obscure classification. The presence of an AGN is simulated by modeling the PSF for Hubble for a variety of images and then inserting a bright source near the center of the galaxy. For each galaxy, the simulated AGN can have one of three colors -- either blue, red, or flat (white) as seen in the color images -- and a range of brightnesses such that $L_\mathrm{ratio} \equiv L_\mathrm{galaxy}/L_\mathrm{AGN}$ is in $(0.2,1.0,2.0,5.0,10.0,50.0)$. Combining these parameters generates 15~images with different simulated AGN for each chosen host.

Images with simulated AGN were classified in the main interface in an identical manner and evenly distributed with unaltered images of the galaxies. Classifiers were not explicitly told that the images had been altered, as the goal was to measure the effect on normal classifications in as unbiased a manner as possible.

Two sets of simulated AGN were measured in GZH. The first set (version~1) was assembled from 95~galaxies from GEMS imaging and PSFs from \texttt{daophot}. The second set (version~2) was assembled from 96~galaxies with GOODS-S imaging; this version used deeper imaging and improved PSFs from \texttt{TinyTim}.

\section{The catalog}

The data release for GZH includes morphological data for 181,101~images (generated from a total of 150,771~unique galaxies). The full table can be accessed at \url{http://data.galaxyzoo.org}. We also include a secondary metadata table, which contains data from a variety of sources explained in Section \ref{sec:data}.

Each image is listed under a unique project ID (eg AHZ000001); the actual galaxy in the image is identified by the combination of the OBJNO and original survey. For each of the 55~responses in the GZH decision tree, the following classification data is provided: for each question, $\tt N_{votes}$ is the number of users to answer that question. For each unique answer, $\tt fraction$ is the fraction of users to select that answer ($\rm N_{answer}/N_{votes}$, and $\tt weighted$ is the weighted fraction, which takes into account user consistency (Section~\ref{sec:weighting}).

@@

We split the data products for GZH by the type of image being classified. Table~\ref{tbl:catalog_hst} contains the classifications for the Hubble images from the AEGIS, COSMOS, and GEMS surveys, as well as 5-epoch deep imaging from the GOODS-N and GOODS-S surveys. This contains 118,425~galaxies and is the primary output from the GZH project. The next two tables have data for a small subset of 3,927~COSMOS~images that were re-processed to study the effect of color balance on morphological classification. Table~\ref{tbl:catalog_faded} has images that are desaturated to minimize the color contrast; Table~\ref{tbl:catalog_recoloured} has images with the red and blue color channels inverted. Table~\ref{tbl:catalog_goods_shallow} contains data for 6,144~galaxies with 2-epoch images from GOODS. These have been mostly supplanted in the main table with deeper 5-epoch GOODS imaging; however, there are 1,683~galaxies in the shallower imaging that were not classified in the deeper mosaics. This data can also be compared to the counterparts in Table~\ref{tbl:catalog_hst} to study the effect of depth on morphological classification. Tables~\ref{tbl:stripe82_single} and \ref{tbl:stripe82_coadd} contain data for the SDSS Stripe~82 single-depth and co-added images, respectively, that were classified using the GZH interface and decision tree. Finally, Table~\ref{tbl:fake_agn} contains classifications for images with artificial point sources intended to simulate the effect of a bright AGN, as used in \citet{sim14}.

\tabletypesize{\scriptsize}
\begin{deluxetable}{lllcrllllll|c}
\centering
\rotate
\tablecolumns{13}
\tablewidth{0pc}
\tablecaption{GZH morphological classifications for Hubble images from AEGIS, COSMOS, GEMS, and GOODS\label{tbl:catalog_hst}} 
\tabletypesize{\scriptsize}
\tablehead{
 & & & 
\multicolumn{2}{c}{\underline{t01\_smooth\_or\_features\_}} &
\multicolumn{6}{c}{\underline{t01\_smooth\_or\_features\_a01\_smooth\_}} &
\colhead{$\ldots$}
\\
\colhead{Project ID} & 
\colhead{Hubble ID} & 
\colhead{Imaging} & 
\colhead{Correction$^{1}$} & 
\colhead{$N_\mathrm{votes}$} & 
\colhead{fraction} & 
\colhead{weighted} & 
\colhead{debiased} & 
\colhead{best} &
\colhead{lower~limit} & 
\colhead{upper~limit} &
\colhead{}
}
\small
\startdata
AHZ100002g  & 10010842  & AEGIS             & 0        & 127       & 0.118    & 0.128     & 0.085    & 0.085    & 0.226     & 0.226    \\
AHZ100002h  & 10010870  & AEGIS             & 4        & 127       & 0.567    & 0.592     & 0.927    & 0.592    & $-$       & $-$      \\
$\ldots$    \\
AHZ20004kd  & 20014731  & COSMOS            & 3        &  44       & 0.682    & 0.675     & 0.147    & 0.675    & $-$       & $-$      \\
AHZ20004ke  & 20014732  & COSMOS            & 2        &  45       & 0.689    & 0.756     & 0.893    & 0.756    & $-$       & $-$      \\
$\ldots$    \\
AHZ400043g  & 90022729  & GEMS              & 1        & 121       & 0.702    & 0.733     & 0.487    & 0.734    & 0.483     & 0.800    \\
AHZ4000416  & 90022735  & GEMS              & 1        & 127       & 0.646    & 0.698     & 0.508    & 0.698    & 0.171     & 0.727    \\
$\ldots$    \\
AGZ0007z47  & 10014     & GOODS-N-FULLDEPTH & 1        & 40        & 0.475    & 0.475     & 0.197    & 0.475    & 0.011     & 0.496    \\
AGZ0007z48  & 10017     & GOODS-N-FULLDEPTH & 3        & 40        & 0.675    & 0.675     & 0.048    & 0.675    & 0.168     & 0.669    \\
$\ldots$    \\
AGZ00083jb  & 8869      & GOODS-S-FULLDEPTH & 1        & 40        & 0.425    & 0.425     & 0.109    & 0.425    & 0.070     & 0.548    \\
AGZ00083jc  & 8878      & GOODS-S-FULLDEPTH & 0        & 40        & 0.205    & 0.205     & 0.048    & 0.048    & $-$0.005  & 0.287    \\
$\ldots$    \\
\enddata
\tablenotetext{1}{Flag indicating how the vote fractions for this galaxy were corrected through debiasing (\S\ref{ssec:zeta_results}), if possible. 0~=~correctable, 1~=~uncorrectable ($p_{raw}$ --- $p_{adj}$ is not single-valued), 2~=~uncorrected ($z_{\rm gal} < 0.3$), 3~=~uncorrectable (insufficient FERENGI galaxies in this $z$-$\mu$ bin), 4~=~uncorrectable (no galaxy redshift available).}
\tablecomments{The full version of this table is available in electronic form, as well as at \url{http://data.galaxyzoo.org}. The complete version includes data for 118,425~galaxies and morphological information for all tasks in the tree. A subset of the information is shown here to illustrate form and content.}
\end{deluxetable}

@@

Needs some test cases for extracting a given set of objects (eg, clump galaxies in a particular redshift range) and evaluation of the results. Possibly include suggested thresholds, \'a la GZ2. 
\section{Using the catalog}
\label{sec:cookbook}
Include cookbook for selecting morphologies.

\section{Analysis}\label{sec:analysis}

@@

\section{Summary}\label{sec:summary}

@@

\begin{table}
\caption{Breakdown of what we can correct out of the GOODS shallow depth data. \label{tbl:goods_shallow_categories}}
\begin{tabular}{lrrrrrrrr}
\hline\hline
                                   & GOODS-N & GOODS-S & Total \\
\hline
Correctable                        & 748     & 514     & 1,262 \\
Uncorrectable                      & 526     & 1,143   & 1,669 \\
No Correction Needed ($z \le 0.3$) & 267     & 267     & 534   \\ 
NEI                                & 851     & 2,670   & 3,521 \\
No Redshift Information            & 159     & 319     & 478   \\
Total                              & 2,551   & 4,913   & 7,464 \\
\hline\hline
\end{tabular}
\end{table}
